Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches

### 2016-06-28 paper/structureScene.tex
revise section IV

In order to achieve invariance to ILD, averaging the left and right channels into a monophonic signal is by far the most widespread approach.
However, it favors the center of the scene while attenuating the presence of lateral sources.
Moreover, sources that are on distinct azimuths get mixed, which may cause bias at training time.
Instead, so as to take advantage of stereophonic data, we perform multiiple combinations of the left channel $\boldsymbol{x_{\mathsf{L}}}(t)$ and right channel $\boldsymbol{x_{\mathsf{R}}}(t)$ into monophonic signals $\boldsymbol{x_{\alpha}}(t)$ according to the equation
\begin{equation}
\boldsymbol{x_{\alpha}}(t) =
\dfrac{1+\alpha}{2} \boldsymbol{x_\mathsf{L}}(t) +
\dfrac{1-\alpha}{2} \boldsymbol{x_\mathsf{R}}(t),
\end{equation}
where $\alpha$ is a panoramic mixing weight, taking values between $-1$ and $+1$, which could be deterministic or random.

In following experiments, we deterministically set $\alpha$ to the values $-1$, $\frac{1}{2}$, $0$, $+\frac{1}{2}$, and $+1$.
This is a form of data augmentation, because $5$ monophonic signals are derived from each binaural recording in the training set.
At test time, only the center mix ($\alpha = 0$) is used to perform a prediction.

@@

%Many approaches coexist for feature selection, including matrix factorization, orthogonal matching pursuit.
This is inspired by the state-of-the-art results of \cite{roma2013}, which rely on cepstral descriptors computed up to a cutoff frequency as small as 900 Hz.

>>>>

In order to achieve invariance to ILD, averaging the left and right channels into a monophonic signal is by far the most widespread approach.
However, it favors the center of the scene while attenuating lateral cues.
Moreover, sources that are on distinct azimuths get mixed, which may cause bias at training time.

Instead, so as to leverage stereophonic data, we perform multiple combinations of the left channel $\boldsymbol{x_{\mathsf{L}}}(t)$ and right channel $\boldsymbol{x_{\mathsf{R}}}(t)$ into monophonic signals $\boldsymbol{x_{\alpha}}(t)$ according to the equation
\begin{equation}
\boldsymbol{x_{\alpha}}(t) =
\dfrac{1+\alpha}{2} \boldsymbol{x_\mathsf{L}}(t) +
\dfrac{1-\alpha}{2} \boldsymbol{x_\mathsf{R}}(t),
\end{equation}
where $\alpha$ is a panoramic mixing weight, taking values between $-1$ and $+1$, which could be deterministic or random.

In following experiments, we deterministically set $\alpha$ to the values $-1$, $\frac{1}{2}$, $0$, $+\frac{1}{2}$, and $+1$.
This is a form of data augmentation, because $5$ monophonic signals are derived from each binaural recording in the training set.
At test time, only the center mix ($\alpha = 0$) is used to perform the class.

@@

This is inspired by the state-of-the-art results of \cite{roma2013}, which rely on cepstral descriptors computed up to a cutoff frequency as small as 900 Hz.
